%======================================================================
\section{Capacitive Wafer-Bias Sheath (m12)}
\label{sec:m12-bias-sheath}
%======================================================================

Mettler's TEL radial [F] measurements (his Fig.~4.13, 4.17) were taken
with a 200\,W RF bias applied to the wafer electrode.  The bias
accelerates positive ions through the wafer sheath, depositing ion
kinetic energy as neutral-gas heating near the wafer, which in turn
expands the plasma glow into the process chamber and raises the local
[F] density by factors of $\sim 1.6$ (90\% SF$_6$) to $\sim 2.15$ (30\%
SF$_6$, centre).  The prior Phase-1 framework had no CCP extension at
all; its omission was documented as Limitation~L5 in the previous
revision.  The present revision adds a dedicated module,
\texttt{m12\_ccp\_bias\_sheath.py}, that closes a reduced-order
Lieberman sheath power balance and couples the result back into the
ionisation source of the ambipolar diffusion solver.

\subsection*{Sheath power balance}

At the wafer ($z=0$), the Bohm ion flux at the sheath edge is
\begin{equation}
  \Gamma_i \;=\; 0.61\,n_{e,\mathrm{wafer}}\,\sqrt{\frac{k_B\,T_e}{m_i}}\,,
  \label{eq:bohm-flux}
\end{equation}
where $m_i$ is a composition-weighted effective ion mass (SF$_5^+$ at
127~amu for 90\% SF$_6$, Ar$^+$ at 40~amu for 30\% SF$_6$).  The
time-averaged sheath DC voltage follows from the bias-power balance:
\begin{equation}
  P_\mathrm{bias} \;=\; e\,V_\mathrm{DC}\,\Gamma_i\,A_\mathrm{wafer}
  \;\;\Rightarrow\;\;
  V_\mathrm{DC} \;=\; \frac{P_\mathrm{bias}}{e\,\Gamma_i\,A_\mathrm{wafer}}\,.
  \label{eq:sheath-Vdc}
\end{equation}
A fraction $f_\mathrm{ion\to gas} = 0.5$ of the ion kinetic power is
deposited as neutral-gas heating near the wafer
(Turner et al.\ 2013~\cite{Turner2013}):
\begin{equation}
  P_\mathrm{ion\to gas} \;=\; f_\mathrm{ion\to gas}\,P_\mathrm{bias}\,.
  \label{eq:ion-to-gas}
\end{equation}

\subsection*{Plasma-glow expansion source}

Instead of resolving a gas-energy PDE (a Phase-3 scope), the module
translates the neutral-heating power into an effective volumetric
ionisation source confined to the process chamber beneath the aperture:
\begin{equation}
  S_\mathrm{bias}(r,z) \;=\; \frac{\lambda_\mathrm{exp}\,P_\mathrm{ion\to gas}}{\varepsilon_T\,e}\,\chi(r,z)\,,
  \label{eq:Sbias}
\end{equation}
where $\chi(r,z)$ is a normalised spatial profile $\int\chi\,dV=1$ that
decays exponentially with distance from the aperture,
$\chi(r,z) \propto \exp\!\bigl(-(z_\mathrm{apt}-z)/L_\mathrm{exp}\bigr)$
for $z \le z_\mathrm{apt}$, with a cosine taper in $r$ bounded by the
wafer radius.  The decay length is $L_\mathrm{exp} = 30$~mm, chosen as
roughly half the process-chamber height.  The dimensionless factor
$\lambda_\mathrm{exp}$ is the one free parameter of the bias model; it
is calibrated once, against Mettler's 90\% SF$_6$ bias-on centre [F]
enhancement of $\times 1.6$, and blind-tested against the 30\% SF$_6$
branch as described below.

\subsection*{Coupling to m11}

The $m12$ output $S_\mathrm{bias}(r,z)$ is added to the ICP-only power
deposition $P_\mathrm{rz}^\mathrm{ICP}(r,z)$ before the ambipolar
diffusion solve:
\begin{equation}
  P_\mathrm{rz}^\mathrm{total}(r,z) \;=\; P_\mathrm{rz}^\mathrm{ICP}(r,z) + P_\mathrm{rz}^\mathrm{bias}(r,z)\,,
\end{equation}
with
$P_\mathrm{rz}^\mathrm{bias}(r,z) = \lambda_\mathrm{exp}\,P_\mathrm{ion\to gas}\,\chi(r,z)$.
When $P_\mathrm{bias} = 0$ (or the module is disabled by configuration),
$S_\mathrm{bias}$ vanishes identically and the framework reduces to the
ICP-only self-consistent pipeline.  See
\texttt{src/dtpm/modules/m12\_ccp\_bias\_sheath.py} for implementation
details.

\subsection*{Calibration and blind test}

The calibration free parameter $\lambda_\mathrm{exp}$ was tuned once
against Mettler's 90\% SF$_6$ bias-on enhancement at 1000\,W, 10\,mTorr,
yielding $\lambda_\mathrm{exp} = 3.20$ and a model enhancement of
$\times 1.61$ (target $\times 1.60$, deviation $+0.8\,\%$).  The same
$\lambda_\mathrm{exp}$ was then applied to the 30\% SF$_6$ case,
producing an enhancement of $\times 1.88$ (target $\times 2.15$,
deviation $-12.8\,\%$).  The blind test deviation lies within the
$\pm 20\,\%$ acceptance band specified in the model design and is a
non-trivial validation: the same calibration captures the opposite
composition regime with the ion mass and electron-temperature
dependence reflected only through the Bohm-flux physics.

The model's mild under-prediction at 30\% SF$_6$ is consistent with a
stronger plasma-volume expansion effect in the more electropositive
(Ar-rich) regime, where the bias sheath extends further before
collisions thermalise the ion beam.  A gas-energy-equation coupling
(Phase-3) would capture this regime difference explicitly; the present
reduced-order calibration over-averages across compositions.

The resulting composition-sensitivity test is summarised in
Fig.~\ref{fig:composition-blind-test}.
