% Replacement abstract for main.tex (around line 50 of the original file).
% Highlights the two architectural upgrades in this revision:
%   - Self-consistent power-coupling efficiency via a Lieberman coupled-circuit
%     model (resolves L6 of the prior revision).
%   - Capacitive wafer-bias sheath module m12 (resolves L5 of the prior revision).

This report presents a \emph{self-consistent Global--2D hybrid framework} ---
a \emph{Unified Masked-Domain Model} --- that couples a validated 0D global
plasma chemistry solver with a two-dimensional axisymmetric
electromagnetic--transport solver on a single shared reactor mask.  The
hybrid architecture is the principal methodological contribution of this
work: a 0D sub-problem supplies volume-averaged electron temperature,
ionisation rates, and gas composition; a 2D sub-problem resolves the induced
azimuthal electric field, Ohmic power deposition, and spatially resolved
electron and radical densities; and a Picard fixed-point iteration returns
spatially averaged 2D quantities back to the 0D closure, driving the coupled
system to self-consistency.  The two solvers share a single axisymmetric
geometry mask that encodes the T-shaped TEL reactor (ICP source tube, 2\,mm
aperture, and processing chamber) and enforces material-specific wall
recombination probabilities following Kokkoris \textit{et al.}\ (2009).

The present revision advances the framework in two architectural directions
relative to the prior Phase-1 release:

\textbf{Self-consistent power coupling.}  The ICP-coil coupling efficiency
$\eta$ is no longer prescribed; it emerges from a Lieberman transformer
coupled-circuit model
$I_\mathrm{peak}^2 = 2\,P_\mathrm{rf}/(R_\mathrm{coil} + R_\mathrm{plasma})$,
where $R_\mathrm{plasma}$ is updated each Picard iteration from the FDTD
Ohmic integral.  The only circuit inputs are $P_\mathrm{rf}$ (user
operating point), $R_\mathrm{coil}$ and $L_\mathrm{coil}$ from
Lieberman~2005 Ch.~12.  Unit tests assert the limiting-case invariants
$\eta \to 1$ at $R_\mathrm{coil}=0$ and $\eta \to 0$ at
$R_\mathrm{plasma}=0$.

\textbf{Capacitive wafer-bias sheath.}  A new module, $m12$, closes a
reduced-order Lieberman sheath power balance at the wafer electrode,
deriving the DC sheath potential, ion flux, and neutral-gas-heating power
from a prescribed bias power.  The result enters the ambipolar diffusion
solver as an effective plasma-volume expansion source in the process
chamber.  A single dimensionless free parameter $\lambda_\mathrm{exp}$ is
calibrated once (on Mettler's 90\,\% SF$_6$ bias-on centre [F]
enhancement) and blind-tested against the 30\,\% SF$_6$ case to verify
composition transferability.

Together these two upgrades allow an \emph{absolute-magnitude} benchmark
against Mettler's (UIUC 2025) spatially resolved radical-probe dataset,
where the prior revision was limited to normalised-shape agreement only.
At Mettler's canonical 1000\,W / 10\,mTorr / 70\,\% SF$_6$ / 200\,W bias
operating point, the converged $\eta \approx 0.95$ and the calibrated
$\lambda_\mathrm{exp} = 3.20$ reproduce his absolute radial [F]
distribution to within the $\pm 20\,\%$ composition-transfer tolerance,
closing the factor-of-2--4 magnitude gap that the prior revision
reported.  Five principal limitations remain (L1-L4 of the architectural
discussion; L5 becomes a kinetic-regime scope note); the previously listed
``prescribed $\eta$'' (old L6) and ``no wafer-bias sheath'' (old L5) are
now resolved in the present revision.
